\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{fontawesome5}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123  -456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape obaida kandakji} \\ \vspace{1pt}
    \small (613)-608-3883 $|$ 
    {\small obaidakandakji@gmail.com} $|$ 
    {\small \href{https://linkedin.com/in/obaidakandakji/}{linkedin.com/in/obaidakandakji/}} $|$
    {\small \href{https://github.com/ObaidaKandakji}{github.com/ObaidaKandakji}}
\end{center}

%-----------Professional Summary---
\section{Professional Summary}
    \begin{itemize}[leftmargin=0.15in, label={}]
      %Motivated Computer Engineering student with hands-on experience in full-stack development, specializing in Python, Java, SQL, and cloud-based technologies. Skilled in building and optimizing scalable software solutions, with knowledge of microservices, data analysis, and DevOps tools like Docker and Kubernetes. Proven ability to work collaboratively in agile environments, delivering high-quality, well-tested code through problem-solving and project-based initiatives. Passionate about continuous learning and eager to contribute to innovative projects that drive real-world impact.
        \small{\item{I am a Computer Engineering graduate with a background in Biochemistry and a genuine interest in how software can solve real-world problems. Currently specializing in Cloud Development, I enjoy the process of learning a tool, whether it’s building autonomous driving simulations in JavaScript or managing infrastructure on Azure, and immediately putting it to work. Years of experience in fast-paced service roles have taught me how to stay organized and collaborate under pressure. I’m looking to bring that same work ethic and a constant learner mindset to an innovative development team.}}
    \end{itemize}



%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:}{ Python, Java, JavaScript, Rust, Go, SQL, C++, HTML/CSS, VHDL, Assembly}\\
     \textbf{Cloud \& Devops:}{ Azure, Docker, Kubernetes, GitHub Actions, Linux, ARM Templates}\\
     \textbf{Frameworks \& Libraries:}{ Node.js, Vue.js, OpenCV, RabbitMQ, MongoDB}\\
     \textbf{Spoken Languages:}{ English, French, Arabic} \\ 
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {Algonquin College}{}
            {Graduate Certificate in Cloud Development and Operations}{September 2025 -- April 2026}
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
        \resumeSubheading
            {University of Ottawa}{}
            {Bachelor of Applied Science in Computer Engineering}{September 2020 -- April 2025}
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
        \resumeSubheading
            {University of Ottawa}{}
            {Bachelor of Science in Biochemistry}{September 2017 -- April 2020}
    \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
    \resumeProjectHeading
          {\textbf{Distributed E-Commerce Microservices Platform} $|$ \emph{Azure AKS, Kubernetes, Docker}}{\href{https://github.com/ObaidaKandakji/CST-8915-Final-Project}{\faGithub\ GitHub}}
            \resumeItemListStart
            \resumeItem{Built a cloud-native e-commerce platform with 5 distributed application components by deploying 2 Vue.js frontends and 3 backend microservices to Azure Kubernetes Service.}
            \resumeItem{Implemented an event-driven order workflow across 3 backend services by routing orders through REST APIs into RabbitMQ and persisting order state in MongoDB for asynchronous processing and admin fulfillment.}
            \resumeItem{Automated CI/CD for 5 services with Docker, GitHub Actions, and kubectl by publishing images to Docker Hub and rolling updates to Azure Kubernetes Service without manual deployment steps.}
          \resumeItemListEnd 

    \resumeProjectHeading
          {\textbf{Neural Network Driving Simulation} $|$ \emph{JavaScript, HTML, CSS}}{\href{https://github.com/ObaidaKandakji/Neural-Network-and-machine-learning-Demo}{\faGithub\ GitHub}}
          \resumeItemListStart
            \resumeItem{Built a self-driving car simulation in JavaScript, HTML, and CSS, implementing neural network logic, vehicle physics, and collision detection from scratch.}
            \resumeItem{Simulated 100 cars at once and improved driving behavior over multiple runs by reusing the best-performing network weights and applying small mutations.}
            \resumeItem{Developed a sensor system and live visualization to show how the car detected its environment and how the neural network responded in real time.}
          \resumeItemListEnd

    \resumeProjectHeading
          {\textbf{AI-Powered Smart Dumbbell System} $|$ \emph{Python}}{\href{https://github.com/nasrAnthony/Capstone-4912}{\faGithub\ GitHub}}
            \resumeItemListStart
            \resumeItem{Developed a real-time postural analysis module using OpenCV to track 15 key body joints, which provided users with immediate feedback and improved exercise form validation accuracy by 30\%.}
            \resumeItem{Applied a Kalman filter to process raw sensor data, reducing signal noise by 40\% and ensuring that repetition counts and movement measurements remained reliable during high-intensity sets.}
            \resumeItem{Collaborated in a team of 7 to build a full-stack web dashboard using Python and SQL, integrating custom machine learning models to provide users with personalized caloric expenditure insights based on their biometric data.}
          \resumeItemListEnd 
          
    \resumeProjectHeading
          {\textbf{Digital Table Management Tool} $|$ \emph{Java, XML, Android Studio}}{}
            \resumeItemListStart
            \resumeItem{Developed a custom Android application using Java and XML to automate seating and busser workflows, which improved communication between servers and support staff reducing table-readiness delays during peak shifts.}
            \resumeItem{Managed the full development lifecycle as a solo developer, from observing operational bottlenecks on the restaurant floor to the final on-site deployment of a centralized digital notification system.}
            \resumeItem{Streamlined front-of-house logistics by replacing manual coordination with a real-time digital solution, resulting in faster guest seating and more efficient staff synchronization in a high-volume environment.}
          \resumeItemListEnd
    
    

    % OPTIONAL_PROJECT_START: Rideau_Canal_Skateway_Real_Time_Monitoring_System
    % \resumeProjectHeading
    %       {\textbf{Rideau Canal Skateway Real-Time Monitoring System} $|$ \emph{Azure Stream Analytics, Cosmos DB, Blob Storage}}{\href{https://github.com/ObaidaKandakji/cst8916-final-project}{\faGithub\ GitHub}}
    %         \resumeItemListStart
    %         \resumeItem{Replaced periodic manual Rideau Canal condition checks with a 5-minute tumbling-window Azure Stream Analytics pipeline, delivering status updates ~97\% faster than manual review cycles.}
    %         \resumeItem{Built stream-processing logic that wrote location-level telemetry aggregates to Cosmos DB and Blob Storage, reducing downstream data-handling effort by ~27\% while preserving operational and historical outputs.}
    %         \resumeItem{Developed safety-classification queries for ice and weather telemetry, turning raw sensor data into dashboard-ready Safe, Caution, and Unsafe status records for each location.}
    %       \resumeItemListEnd
    % OPTIONAL_PROJECT_END: Rideau_Canal_Skateway_Real_Time_Monitoring_System
    \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Server}{Sept 2018 -- Present}
      {Cora's}{}
      \resumeItemListStart
        \resumeItem{Managed busy section of several tables at once, multitasking between taking orders and checking in on guests to ensure everyone is served quickly and accurately.}
        \resumeItem{Worked closely with the kitchen and other servers to stay organized during the morning rush, helping the team stay on track so every guest has a smooth dining experience.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

%    \resumeSubheading
%      {Computer Technician}{June 2019 -- Present}
%      {Self}{}
%      \resumeItemListStart
%        \resumeItem{Designed and assembled custom high-performance computers, tailored to client specifications, increasing system efficiency and performance by 10\%.}
%        \resumeItem{Performed comprehensive testing and quality assurance on all builds, ensuring optimal functionality and extended system longevity.}
%    \resumeItemListEnd

  \resumeSubHeadingListEnd

\end{document}
